Open archaeology, open source?

### 2024-02-06 analysis/_03-data_methodology.qmd
Update to open-archaeo 2024-02-6

We opted to only collect repository data from GitHub because it is the most popular forge platform used by open-archaeo projects (@tbl-forges).
This means that projects that do not use version control (`r percent(p_no_vc)` of the total), or host it elsewhere (`r percent(p_no_github)` of the total), are excluded from these parts of the analysis, though we were still able to perform an analysis of their contents and authorship from the data included in open-archaeo itself.
We also exclude collaboration through offline or private channels, or forms of collaboration we do not know about. 
We did not directly observe or interview archaeological software developers, though our conclusions do draw heavily from our experience as members of that community ourselves. 
Our earliest data is from 2005 and our study can say little about collaborative software development in archaeology before this point, though we know there was a significant amount of it [@ducke2013 ; @whallon1972].

>>>>

We opted to only collect repository data from GitHub because it is the most popular forge platform used by open-archaeo projects (@tbl-forges).
This means that projects that do not use version control (`r percent(p_no_vc)` of the total), or host it elsewhere (`r percent(p_no_github)` of the total), are excluded from these parts of the analysis, though we were still able to perform an analysis of their contents and authorship from the data included in open-archaeo itself.
We also exclude collaboration through offline or private channels, or forms of collaboration we do not know about. 
We did not directly observe or interview archaeological software developers, though our conclusions do draw heavily from our experience as members of that community ourselves. 
Our earliest data is from 2005 and our study can say little about collaborative software development in archaeology before this point, though we know there was a significant amount of it [@ducke2013; @whallon1972].
